Concave reduction of swarm voids

### 2018-02-24 paper.tex
Graph error fix

Equation~\eqref{eq:ConcaveVoidPhysics1} generates the dictionary set of all the neighbours along with an angle that each of the agent’s neighbour’s make with the first detected neighbour. $nbr(b)$ returns a set of all an agents neighbours.

@@

\ref{concave:BaselineConcaveEffectPath2} shows a more detailed view of the structure within the swarm. The baseline (black) paths show the swarm expanding and then settling to a hexagonal pattern which appears to oscillate slightly (jitter) when the swarm has reached its optimum distribution. The concave reduction swarm agents paths (red) show the swarm expanding in a similar way but once fully expanded the concave reduction causes the swarm to move with a slight directional bias.

@@

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{figures/Baseline8060End}
\end{center}
\caption{Baseline end\label{fig:BaselineEndPoint}}
\end{figure}

@@

%COVERBASELINE4560-BASEEND.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/Baseline4560End}
{Baseline end\label{fig:BaselineEndPoint4560}}

@@

%COVERBASELINE4560END3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/Concave4560End}
{Concave end\label{fig:ConcaveEndPoint4560}}

@@

%COVERBASELINE4560END1.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/Concave4560-1}
{Initial\label{fig:VoidConcaveReduction1}}

@@

%COVERBASELINE4560END2.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/Concave4560-2}
{Partial\label{fig:VoidConcaveReduction2}}

@@

%COVERBASELINE4560END3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/Concave4560-3}
{Complete\label{fig:VoidConcaveReduction3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/OilSpillBase1}
{Initial\label{concave:OilSpillBase1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/OilSpillBase2}
{Partial\label{concave:OilSpillBase2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/OilSpillBase3}
{End\label{concave:OilSpillBase3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/OilSpillConcave1}
{Initial\label{concave:OilSpillConcave1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/OilSpillConcave2}
{Partial\label{concave:OilSpillConcave2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/OilSpillConcave3}
{End\label{concave:OilSpillConcave3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=6cm]{figures/IdealSwarm}
{Swarm structure with no concave reduction\label{voids:IdealSwarm}}

\begin{figure}
\begin{center}
\includegraphics[width=6cm]{figures/IdealSwarm}
\end{center}
\caption{Swarm structure with no concave reduction\label{voids:IdealSwarm}}
\end{figure}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Images/NEGrey}}]{Neil Eliot}
is a Senior Lecturer at Northumbria University.  Neil was awarded his Ph.D. from Northumbria in 2017, his Pg.C. in 1994, and his B.Sc. in 1989 all in Computing. His research areas include swarm theory and cybersecurity. Neil is a Certified Ethical Hacker (CEH) and coordinator for the EC Council Academic alliance at Northumbria. Prior to this Neil worked in the chemical industry and the NHS. His research interests are in the area of network cybersecurity, smart home technologies and swarm theory. 
\end{IEEEbiography}

>>>>

Equation~\eqref{eq:ConcaveVoidPhysics1} generates the dictionary set of all the neighbours along with an angle that each of the agent's neighbour's make with the first detected neighbour. $nbr(b)$ returns a set of all an agents neighbours.

@@

Figure~\ref{concave:BaselineConcaveEffectPath2} shows a more detailed view of the structure within the swarm. The baseline (black) paths show the swarm expanding and then settling to a hexagonal pattern which appears to oscillate slightly (jitter) when the swarm has reached its optimum distribution. The concave reduction swarm agents paths (red) show the swarm expanding in a similar way but once fully expanded the concave reduction causes the swarm to move with a slight directional bias.

@@

%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/Baseline8060End}
%% \end{center}
%% \caption{Baseline end\label{fig:BaselineEndPoint}}
%% \end{figure}

@@

%COVERBASELINE4560-BASEEND.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/Baseline4560End}
{Baseline end\label{fig:BaselineEndPoint4560}}

@@

%COVERBASELINE4560END3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/Concave4560End}
{Concave end\label{fig:ConcaveEndPoint4560}}

@@

%COVERBASELINE4560END1.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/Concave4560-1}
{Initial\label{fig:VoidConcaveReduction1}}

@@

%COVERBASELINE4560END2.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/Concave4560-2}
{Partial\label{fig:VoidConcaveReduction2}}

@@

%COVERBASELINE4560END3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/Concave4560-3}
{Complete\label{fig:VoidConcaveReduction3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/OilSpillBase1}
{Initial\label{concave:OilSpillBase1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/OilSpillBase2}
{Partial\label{concave:OilSpillBase2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/OilSpillBase3}
{End\label{concave:OilSpillBase3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/OilSpillConcave1}
{Initial\label{concave:OilSpillConcave1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/OilSpillConcave2}
{Partial\label{concave:OilSpillConcave2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/OilSpillConcave3}
{End\label{concave:OilSpillConcave3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=3cm]{figures/IdealSwarm}
{Swarm structure with no concave reduction\label{voids:IdealSwarm}}

%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=6cm]{figures/IdealSwarm}
%% \end{center}
%% \caption{Swarm structure with no concave reduction\label{voids:IdealSwarm}}
%% \end{figure}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Images/NEGrey}}]{Neil Eliot}
is a Senior Lecturer at Northumbria University.  Neil was awarded his Ph.D. from Northumbria in 2017, his Pg.C. in 1994, and his B.Sc. in 1989 all in Computing. His research areas include swarm theory and cybersecurity. Prior to this Neil worked in the chemical industry and the NHS. His research interests are in the area of network cybersecurity, smart home technologies and swarm theory. 
\end{IEEEbiography}
